---
title: "COMPSCIX 415.2 Homework 9/Final"
author: "Michelle Nie"
date: "3/31/19"
output:
  html_document:
    df_print: paged
---
# Question 1

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(broom)

# sample size
samp_size <- 100
# set the rate parameter
samp_rate <- 1/10000

# take sample
rexp(n = samp_size, rate = samp_rate)

```
 
## Step 1 
 
```{r}
samp_fun <- function(samp_size, samp_rate) {
  sample <- rexp(samp_size, samp_rate)
  samp_avg <- mean(sample)
  samp_std_dev <- sd(sample)
  stats <- list(samp_avg = samp_avg, samp_std_dev = samp_std_dev)
  return(stats)
}

# test
samp_fun(1000,0.5)
```

## Step 2
```{r}

sample_means <- rep(NA, 1000)

sample_sds <- rep(NA, 1000)


for (i in 1:1000) {
  samp_fun_vector <- samp_fun(50, 1/10000) 
  sample_means[i] <- samp_fun_vector$samp_avg
  sample_sds[i] <- samp_fun_vector$samp_std_dev
}

sample_means <- as.data.frame(sample_means)

head(sample_means)

```


## Step 3

```{r}
ggplot(sample_means) + 
  geom_histogram(mapping = aes(sample_means))

std_dev <- sapply(sample_means, sd, na.rm = TRUE)

theoretical_std_error <- std_dev / sqrt(50)

mean <- sapply(sample_means, mean, na.rm = TRUE)

empirical_std_error <- mean / sqrt(50)

std_dev
theoretical_std_error
mean
empirical_std_error
```


## Step 4

```{r}

sample_means_5000 <- rep(NA, 1000)

sample_sds_5000 <- rep(NA, 1000)


for (i in 1:1000) {
  samp_fun_vector_5000 <- samp_fun(5000, 1/10000) 
  sample_means_5000[i] <- samp_fun_vector_5000$samp_avg
  sample_sds_5000[i] <- samp_fun_vector_5000$samp_std_dev
}

sample_means_5000 <- as.data.frame(sample_means_5000)


ggplot(sample_means_5000) + 
  geom_histogram(mapping = aes(sample_means_5000))

std_dev_5000 <- sapply(sample_means_5000, sd, na.rm = TRUE)

theoretical_std_error_5000 <- std_dev_5000 / sqrt(5000)

mean_5000 <- sapply(sample_means_5000, mean, na.rm = TRUE)

empirical_std_error_5000 <- mean / sqrt(5000)


std_dev_5000
theoretical_std_error_5000
mean_5000
empirical_std_error_5000

```


# Question 2


```{r}
train <- read.csv("/Users/Michelle/Desktop/compscix-415-2/train.csv")

train_lm <- lm(formula = SalePrice ~ LotArea + OverallQual + ExterQual, data = train)
tidy(train_lm)
glance(train_lm)


```


- Coefficient on LotArea: 1.45 - for every one unit increase in LotArea (in sqft), the sale price increases by $1.45. 
- Coefficient on ExterQualGd: 71,529.50 -  compared to ExterQualEx (a house with excellent quality of the material on the exterior), a house with a good quality of exterior material is $71,529.50 cheaper. 
- The adjusted r-squared value in HW 7 was 0.783. The adjusted r-squared value here is 0.694. This means that the HW 7 model was a better fit than this current model.


# Question 3

```{r}
ab_test <- read.csv("/Users/Michelle/Desktop/compscix-415-2/ab_test_data.csv")

```

## a)
The conversion rate for A is 0.0415 (83/2000) and the conversion rate for B is 0.1 (200/2000).

## b) 

```{r}
true_a <- 0.0415
true_b <- 0.1
n_a <- 2000
n_b <- 2000

set.seed(10)
samp_a <- rbinom(n = 1, size = n_a, prob = true_a)
samp_b <- rbinom(n = 1, size = n_b, prob = true_b)


samp_a
samp_b

proptest <- prop.test(c(samp_a, samp_b), c(2000, 2000))
proptest$p.value


```

The p-value is 1.25388e-10.