---
title: "COMPSCIX 415.2 Homework 3"
author: "Michelle Nie"
date: "2/12/19"
---

```{r warning=FALSE, message=FALSE}
library(nycflights13)
library(tidyverse)
```

# 3.8.1 Exercises

## 1) What is the problem with this plot? How could you improve it?

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```

- The problem with this plot is that hwy and cty are so closely correlated that the plot looks messy.
- I would instead use a smooth line chart like below:


```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_smooth()
```

## 2) What parameters to geom_jitter() control the amount of jittering?

- Width and Height control the amount of jittering (vertical and horizontal jitter, respectively).


## 3) Compare and contrast geom_jitter() with geom_count().


```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter()

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_count()

```

- geom_jitter() and geom_count() both create scatterplots that attempt to point out overlapping points. However, geom_count() produces points of different sizes corresponding to the number of instances of each observation at each location, and it produces a legend for the different sizes. On the other hand, geom_jitter() simply jitters overlapping points around slightly so that they do not overlap.


## 4) What’s the default position adjustment for geom_boxplot()? Create a visualisation of the mpg dataset that demonstrates it.

```{r}

ggplot(data = mpg) + 
  geom_boxplot(mapping = aes(x = drv, y = hwy, fill = class)) +
  ggtitle("default")


ggplot(data = mpg) + 
  geom_boxplot(mapping = aes(x = drv, y = hwy, fill = class), position = "dodge") +
  ggtitle("dodge")


ggplot(data = mpg) + 
  geom_boxplot(mapping = aes(x = drv, y = hwy, fill = class), position = "identity") +
  ggtitle("identity")


ggplot(data = mpg) + 
  geom_boxplot(mapping = aes(x = drv, y = hwy, fill = class), position = "jitter") +
  ggtitle("jitter")
```

- The default position adjustment for geom_boxplot() is "dodge" - the resulting graph looks nearly identical to the default graph.


# Section 3.9.1: #2 and #4 only

## 2) What does labs() do? Read the documentation.

- labs() creates labels for plots, such as the title, x-axis label, and y-axis label.

## 4) What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() 

```

- The plot tells you that cty and hwy have a positive correlation with a slope > 1.
- coord_fixed() is important because it fixes the aspect of the plot so that it is 1:1. This prevents the skewing of data by distorting axes.
- geom_abline() creates a reference line on the plot. By default the slope is 1.


# Section 4.4: #1 and #2 only

## 1) Why does this code not work?

- The second "my_varıable" actually includes a dotless "i", or "ı".


## 2) Tweak each of the following R commands so that they run correctly:

```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8) # fixed typo in filter, added double equal sign
filter(diamonds, carat > 3) # fixed typo in diamonds
```

# Section 5.2.4: #1, #3 and #4 only.

<<<<<<< HEAD
=======
# Section 5.2.4: #1, #3 and #4 only

>>>>>>> fac171ab71d6a3ccbf2d0ccdde0d741a19ad8b66
## 1) Find all flights that

### Had an arrival delay of two or more hours

```{r}
<<<<<<< HEAD
library(tidyverse)
library(nycflights13)

filter(flights, arr_delay >= 120)
```

=======
library(nycflights13)

filter(flights, arr_delay >= 120)

```
>>>>>>> fac171ab71d6a3ccbf2d0ccdde0d741a19ad8b66


### Flew to Houston (IAH or HOU)

```{r}
filter(flights, dest %in% c("IAH", "HOU"))
```

<<<<<<< HEAD
=======

>>>>>>> fac171ab71d6a3ccbf2d0ccdde0d741a19ad8b66
### Were operated by United, American, or Delta

```{r}
filter(flights, carrier %in% c("UA", "AA", "DL"))
```

### Departed in summer (July, August, and September)

```{r}
filter(flights, month %in% c(7,8,9))
```

### Arrived more than two hours late, but didn’t leave late

```{r}
<<<<<<< HEAD
filter(flights, month %in% c(7,8,9))
```

### Were delayed by at least an hour, but made up over 30 minutes in flight
### Departed between midnight and 6am (inclusive)
=======
filter(flights,
       arr_delay > 120,
       dep_delay == 0)
```

### Were delayed by at least an hour, but made up over 30 minutes in flight

```{r}
filter(flights,
       dep_delay >= 60,
       arr_delay <= -30)
```

### Departed between midnight and 6am (inclusive)

```{r}
filter(flights, dep_time <= 0600)
```

## 3) How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

- 8,255 flights have a missing dep_time. 
- Other variables that are missing are dep_delay, arr_time, arr_delay, and air_time.
- These rows most likely represent flights that were canceled.

```{r}
filter(flights, is.na(dep_time))
```



## 4) Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)

```{r}
NA ^ 0
```

- The above is not missing because anything to the power of 0 is 1, even if it is a null/missing value.

```{r}
NA | TRUE

```

- The above is not missing because the expression evaluates to TRUE if either side of the "|" evaluates to TRUE. 

```{r}
FALSE & NA
```

- The above evaluates to FALSE because the outcome can be evaluated with incomplete information. If one of the values is missing, it can still evaluate to FALSE.

- My prediction of the general rule: 
-- Anything to the power of 0 is 1. 
-- When `NA is used in an OR operator with TRUE, it can evaluate to TRUE. When it is used in an AND operator with FALSE, it can evaluate to FALSE. If you switch the operators in either scenario, the expressions will evaluate to NA.


# Section 5.4.1: #1 and #3 only

## 1) Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.

```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
```

```{r}
select(flights, dep_time:arr_delay, -sched_dep_time, -sched_arr_time)
```

```{r}
select(flights, 
       starts_with("dep"),
       starts_with("arr")
)
```


```{r}
select(flights, 
       dep_time, arr_time,
       ends_with("delay")
)
```

```{r}
select(flights, 
       ends_with("delay"),
       ends_with("time"),
       -(contains("sched")),
       -(contains("air"))
)
```


## 3) What does the `one_of()` function do? Why might it be helpful in conjunction with this vector?

- According to the help article, `one_of()` matches variable names in a character vector.
- It can be useful because you can select multiple columns by storing it in a variable and calling it with `one_of()`. 


```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")

select(flights, one_of(vars))

```




>>>>>>> fac171ab71d6a3ccbf2d0ccdde0d741a19ad8b66
