---
title: "COMPSCIX 415.2 Homework 4"
author: "Michelle Nie"
date: "2/20/19"
output:
  html_document:
    df_print: paged
---

# Section 5.6.7: #2, #4 and #6 only. Extra Credit: Do #5

## 2a) 
```{r}
library(tidyverse)
library(nycflights13)

not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))


not_cancelled %>% count(dest)
```

- Another approach:

```{r}
not_cancelled %>% 
  group_by(dest) %>% 
  summarize(n = n())
```

## 2b)

```{r}
not_cancelled %>% count(tailnum, wt = distance)
```

- Another approach: 

```{r}
not_cancelled %>% 
  group_by(tailnum) %>% 
  summarize(n = n())
```

## 4) Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?


```{r}
cancelled <- flights  %>% 
  filter(is.na(dep_delay), is.na(arr_delay))

by_day <- cancelled %>% 
  group_by(day) %>% 
  summarize(num_cancelled = n())

by_day

by_month <- cancelled %>% 
  group_by(month) %>% 
  summarize(num_cancelled = n())

by_month
```

- There does not appear to be a pattern in the number of cancelled flights by day or month.

```{r}
cancelled %>% 
  group_by(year,month, day) %>% 
  summarize(prop = mean(arr_delay > 0))
```



## 6) What does the sort argument to count() do. When might you use it?

```{r}

```



## Extra Credit - 5)

# Section 10.5: #1, #2, #3 and #6 only
# Section 12.3.3: #2, #3 and #4 only
# Section 12.4.3: #1 and #2 onl 