---
title: "COMPSCIX 415.2 Homework 7"
author: "Michelle Nie"
date: "3/14/19"
output:
  html_document:
    df_print: paged
---

# Exercise 1


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)

train <- read.csv("C:/Users/mnie/Documents/RClass_Desktop/compscix-415-2-assignments-new/train.csv")

train
```

- There are 1,460 observations and 81 columns.

# Exercise 2:

```{r}
ggplot(train) +
  geom_histogram(mapping = aes(SalePrice))


ggplot(train) +
  geom_point(mapping = aes(SalePrice, Neighborhood))


ggplot(train) +
  geom_point(mapping = aes(SalePrice, OverallQual))

```


# Exercise 3:

```{r}
(saleprice_lm <- lm(formula = SalePrice ~ SalePrice, data = train))
tidy(saleprice_lm)

SalePrice_avg <- mean(train$SalePrice)

glance(saleprice_lm)


```


- The coefficient is $180,921  and the average value of SalePrice is $180,921.20, so they are approximately equal to each other.
- The r-squared is 0



# Exercise 4:

```{r}
(saleprice_mult_lm <- lm(formula = SalePrice ~ GrLivArea + OverallQual + Neighborhood, data = train))
tidy(saleprice_mult_lm)

glance(saleprice_lm)

 BrkSide_avg <- train %>% 
   filter(Neighborhood == "BrkSide") %>% 
   summarize(mean(SalePrice)) 
 
 SalePrice_avg <- mean(train$SalePrice)
 
 SalePrice_avg - BrkSide_avg

```

- GrLivArea: For every one unit increase in square footage, the sale price increases, on average, by $55. The p-value is extremely small (2e-94), so the coefficient is significant. However, this coefficient may not be practically significant because the sale price increase is only $55. 
- OverallQual: For every one unit increase in OverallQual, the sale price increases, on average, by $20,951. The p-value is also extremely small (1e-65), so the coefficient is significant. I believe this coefficient is practically significant because it is a meaningful predictor of sale price. 
- NeighborhoodBrkSide: The average sale price is $13,025 less than the average. The p-value is approximately 0.2, which means it is somewhat significant. 

- The model is not a good fit because the r-squared value is 0.


# Exercise 6

```{r}
sim1a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)
sim1a_lm <- lm(formula = y ~ x, data = sim1a)
tidy(sim1a_lm)
glance(sim1a_lm)


sim1b <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)
sim1b_lm <- lm(formula = y ~ x, data = sim1b)
tidy(sim1b_lm)
glance(sim1b_lm)


sim1c <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)
sim1c_lm <- lm(formula = y ~ x, data = sim1c)
tidy(sim1c_lm)
glance(sim1c_lm)


sim1d <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)
sim1d_lm <- lm(formula = y ~ x, data = sim1d)
tidy(sim1d_lm)
glance(sim1d_lm)


sim1e <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)
sim1e_lm <- lm(formula = y ~ x, data = sim1e)
tidy(sim1e_lm)
glance(sim1e_lm)

```


- The coefficient of x varies, but ranges from 1.26 to 1.77
- There is less variance around the r-squared value - it tends to be around 0.8 every time, meaning this model is likely a good fit.













