---
title: "COMPSCIX 415.2 Homework 3"
author: "Michelle Nie"
date: "2/12/19"
---

```{r warning=FALSE, message=FALSE}
library(nycflights13)
library(tidyverse)
```

# 3.8.1 Exercises

## 1) What is the problem with this plot? How could you improve it?

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```

- The problem with this plot is that hwy and cty are so closely correlated that the plot looks messy.
- I would instead use a smooth line chart like below:


```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_smooth()
```

## 2) What parameters to geom_jitter() control the amount of jittering?

- Width and Height control the amount of jittering (vertical and horizontal jitter, respectively).


## 3) Compare and contrast geom_jitter() with geom_count().


```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter()

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_count()

```

- geom_jitter() and geom_count() both create scatterplots that attempt to point out overlapping points. However, geom_count() produces points of different sizes corresponding to the number of instances of each observation at each location, and it produces a legend for the different sizes. On the other hand, geom_jitter() simply jitters overlapping points around slightly so that they do not overlap.


## 4) What’s the default position adjustment for geom_boxplot()? Create a visualisation of the mpg dataset that demonstrates it.

```{r}

ggplot(data = mpg) + 
  geom_boxplot(mapping = aes(x = drv, y = hwy, fill = class)) +
  ggtitle("default")


ggplot(data = mpg) + 
  geom_boxplot(mapping = aes(x = drv, y = hwy, fill = class), position = "dodge") +
  ggtitle("dodge")


ggplot(data = mpg) + 
  geom_boxplot(mapping = aes(x = drv, y = hwy, fill = class), position = "identity") +
  ggtitle("identity")


ggplot(data = mpg) + 
  geom_boxplot(mapping = aes(x = drv, y = hwy, fill = class), position = "jitter") +
  ggtitle("jitter")
```

- The default position adjustment for geom_boxplot() is "dodge" - the resulting graph looks nearly identical to the default graph.


# Section 3.9.1: #2 and #4 only

## 2) What does labs() do? Read the documentation.

- labs() creates labels for plots, such as the title, x-axis label, and y-axis label.

## 4) What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() 

```

- The plot tells you that cty and hwy have a positive correlation with a slope > 1.
- coord_fixed() is important because it fixes the aspect of the plot so that it is 1:1. This prevents the skewing of data by distorting axes.
- geom_abline() creates a reference line on the plot. By default the slope is 1.


# Section 4.4: #1 and #2 only

## 1) Why does this code not work?

- The second "my_varıable" actually includes a dotless "i", or "ı".


## 2) Tweak each of the following R commands so that they run correctly:

```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8) # fixed typo in filter, added double equal sign
filter(diamonds, carat > 3) # fixed typo in diamonds
```

# Section 5.2.4: #1, #3 and #4 only.

## 1) Find all flights that

### Had an arrival delay of two or more hours

```{r}
library(tidyverse)
library(nycflights13)

filter(flights, arr_delay >= 120)
```



### Flew to Houston (IAH or HOU)

```{r}
filter(flights, dest %in% c("IAH", "HOU"))
```

### Were operated by United, American, or Delta

```{r}
filter(flights, carrier %in% c("UA", "AA", "DL"))
```

### Departed in summer (July, August, and September)

```{r}
filter(flights, month %in% c(7,8,9))
```

### Arrived more than two hours late, but didn’t leave late

```{r}
filter(flights, month %in% c(7,8,9))
```

### Were delayed by at least an hour, but made up over 30 minutes in flight
### Departed between midnight and 6am (inclusive)
